Cluster Difference Imaging Photometric Survey (CDIPS) II: A Jupiter-Sized Planet in IC~2602

### 2020-05-15 paper/ms.tex
paper: add some comments on BEBs and NEBs

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f6.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Spectral energy distribution of \tn\ from archival
    photometry.}
    {\bf Keivan: please describe!}
    \label{fig:sed}
	}
\end{figure}

@@

@@

  \item {\it Background blends}.
  Archival imaging (POSS) available in the south?
\end{itemize}

>>>>

\begin{figure}[t!]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f6.png}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Spectral energy distribution of \tn\ from archival
    photometry.}
    {\bf Keivan: please describe, and if possible, send me the data
    (photometry + the atmosphere model) used to generate the plot so I
    can regenerate it in a consistent style with the rest of the paper}
    \label{fig:sed}
	}
\end{figure}

@@

Given its galactic latitude of only $-6^\circ$, it is not surprising
that the field of \tn\ is crowded.
A number of possible false-positive explanations, including
the usual neighboring, background, and hierarchical eclipsing binary
scenarios, must therefore be considered.

For these scenarios to be viable, the flux from \tn\ and the true
eclipsing binary host would blend together, reducing the ``true''
eclipse depth $\delta_{\rm true}$ to produce the observed depth
$\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm neighbor}}{F_{\rm total}},
\end{equation}
where the total flux and the flux from the neighbor are labelled as
such.
The requirement that the true eclipse depth is less than one
translates to a bound on the faintest possible blended companion
stars:
\begin{equation}
    \Delta m < - \frac{5}{2} \log_{10} \delta_{\rm obs}.
\end{equation}
For \tn\ ($T=9.93$), this implies that any star invoked to explain the
transit depth must be brighter than $T=15.92$.

% TODO: there's an even stronger argument advanced by Vanderburg et al
% (2019), and used by Rizzuto+2020.
There's also
\begin{equation}
  \Delta m <
  -\frac{5}{2} \log_{10} (\delta_{\rm obs} t_{12}^2/t_{13}^2).
\end{equation}

@@

  \item {\it Background blends}.
    Archival SERC-J and AAO-SES plates are available for the \tn\
    field\footnote{\url{https://archive.stsci.edu/cgi-bin/dss_form}}.
    These plates were acquired in 1982 and 1992, respectively.
    For high proper motion stars archival imagery can be used to
    detect slowly moving background stars that might be an
    astrophysical false-positive source
    ({\it e.g.}, \citealt{huang_pimen_2018}).
    However \tn\ has only moved $\approx0.7''$ between 1982 and
    present, in comparison to the $\approx2.0''$ FWHM of the target on
    the plates.
    We therefore cannot resolve it with great confidence from
    background sources not already resolved through more modern
    imaging.

\end{itemize}
